Fixing Vulnerabilities Hinders Maintainability

### 2019-02-04 paper/ICPC19/icpc19.tex
cf figure

One of the guidelines with which the project does not comply is the one presented in the report (Figure~\ref{fig:bchrep}): \emph{Write Simple Units of Code}. SIG defines \emph{Units} as the smallest groups of code that can be maintained and executed independently~\cite{Visser:2016:OREILLY} (e.g., methods and constructors in Java).

>>>>

\Luis{(Figure -- (cf. Figure [mesmo para outras refs semelhantes que estao por
ai espalhadas]}
One of the guidelines with which the project does not comply is
the one presented in the report (Figure~\ref{fig:bchrep}): \emph{Write Simple
Units of Code}. SIG defines \emph{Units} as the smallest groups of code that
can be maintained and executed independently~\cite{Visser:2016:OREILLY} (e.g.,
methods and constructors in Java).
